---
output:
  pdf_document: default
  html_document: default
---
Exploring Loan Data by Wessam Alhallak
========================================================

---
title: "Exploring Loan Data"
author: "Wessam Alhallak"
date: "11 März 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

#install.packages("devtools")
#install_github("clauswilke/ggridges")
library(devtools)
library(ggplot2)
library(ggridges)
library(plyr)
library(GGally)
library(gridExtra)
library(dplyr)
library(reshape2)
library(alr3)
library(forcats)
library(RColorBrewer)
library(viridis)
library(Hmisc)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, load_data}
# Load the Data
RawData<-read.csv("prosperLoanData.csv")
Variable<-read.delim(file="prosperLoanData_variables.tsv")
RawData$ListingCreationDate<-
  as.POSIXct(RawData$ListingCreationDate,format="%Y-%m-%d %H:%M:%S")
```

This data set contains 113,937 loans with 81 variables on each loan,including loan amount,borrower rate (orinterest rate), currentloan status, borrowerincome, borroweremployment status,borrower credit history,and the latest paymentinformation.
And I will list my interested Variables  after reading the descriptions of each varaibles



```{r message=FALSE, warning=FALSE, packages}

intData=RawData%>%select(ListingCreationDate,
                         Term,
                         LoanStatus,
                         IncomeRange,
                         BorrowerRate,
                         ProsperRating..Alpha.,
                         Occupation,
                         EmploymentStatus,
                         EmploymentStatusDuration,
                         DebtToIncomeRatio,
                         IncomeRange,
                         LoanOriginalAmount,
                         LP_InterestandFees,
                         Investors)
```

#Scatter matrix and first overview
Here we will make an overview for all variable together then 
we will try to explore variables as univariable to know some information about
the chartatsitic for each variable , later on we will try to explore some information
about the realtion between each two variables and then we try to get in depth between more
than two variables in mulitvariable section finally I will reflect my conclusinios in 
the last section #conclusion

```{r  message=FALSE, warning=FALSE, paged.print=TRUE}
ggpairs(intData[sample.int(nrow(intData),1000),],cardinality_threshold=100)

```

# Univariate Plot


```{r}


ggplot(data=RawData,aes(x=ListingCreationDate))+
  geom_histogram(bins=200,fill="#567456")+
  theme(axis.text.x = element_text(size=10),
          axis.text.y = element_text(size=10, angle=45))+
  labs(title="Listing Creation Date  ",
       subtitle="The date the listing was created.",
       y="Count")
```


```{r}
Occupation_group<- 
  group_by(RawData,Occupation)

RawData.Occupation_group<-
  summarise(Occupation_group,count=n())

RawData.Occupation_group<-
  arrange(RawData.Occupation_group,-(count))



ggplot(data = head(RawData.Occupation_group,10),
       aes(x= reorder(Occupation, -count), 
           y=count))+
  geom_bar(stat = "identity")+
  theme(axis.text.x = element_text(size=10, angle=45,hjust = 1))+
  labs(title="Occupation ",
       subtitle="The Occupation selected by the Borrower at the time they created the listing.",
       x="Occupation",
       y="Count")

```

```{r}
```


```{r eval=FALSE, include=FALSE}

##aes(x=reorder(Position, -table(Position)[Position]))

#ggplot(data=RawData,aes(x=reorder(Occupation, -table(Occupation)[Occupation])))+
#  geom_bar()+
#  coord_trans(y="sqrt")+
  #ylim(500,100000)+
  #theme(axis.text.x = element_text(size=6, angle=90,hjust = 1))+
  #labs(title="Occupation ",
       #subtitle="The Occupation selected by the Borrower at the time they created the listing.",
       #x="Occupation",
       #y="Count")



#RawData %>%
#  count(Occupation) %>%
#  filter(n > quantile(n,0.85)) %>%
#  ggplot(aes(x = reorder(Occupation,-n), y = n)) +
#    geom_bar(stat = "identity") + theme_minimal() +
#    theme(axis.text.x = element_text(size = 10, angle= 45, hjust=1))+
#    labs(title="Occupation ", x="Occupation", y="Count")

  

```



```{r}
RawData %>% count(Occupation) %>% 
  mutate(Occupation=reorder(Occupation,-n))%>% 
  filter(n>quantile(n,0.80))%>%
  ggplot(aes(Occupation, y = n,fill=sqrt(n)))+
    geom_bar(stat = "identity")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = 10, angle= 45, hjust=1))+
  labs(title="Occupation ", x="Occupation", y="Count",fill="Sqrt(Count)")
```


```{r}

RawData %>%
  #mutate(as.factor(Term))%>%
  #count(Term) %>% 
  ggplot(aes(x=as.factor(Term)))+
    geom_bar()+
    coord_trans(y='sqrt')+
    theme_minimal()+
    theme(axis.text.x = element_text(size = 24))+
    labs(title="Term", x="Term", y="Count")
  
```

```{r}
loanstat=RawData$LoanStatus
RawData %>%
  count(LoanStatus) %>% 
  mutate(LoanStatus=reorder(LoanStatus,-n))%>% 
  #filter(n>quantile(n,0.20))%>%
  ggplot(aes(x=LoanStatus, y = sqrt(n),fill=sqrt(n)))+
    geom_bar(stat = "identity")+
    #coord_trans(x='sqrt')+
    #coord_polar()+
    scale_fill_viridis(option = "A")+
    theme_minimal()+
    theme(axis.text.x = element_text(size =8, angle= 45, hjust=1))+
    labs(title="Loan Status Count ", x="Loan Status", y="Count",fill="Sqrt(Count)")
```

```{r}
IncomeRange=RawData$IncomeRange
RawData %>%
  count(IncomeRange) %>% 
  #mutate(IncomeRange=reorder(IncomeRange,-n))%>% 
  #filter(n>quantile(n,0.20))%>%
  ggplot(aes(x=IncomeRange, y = n,fill=sqrt(n)))+
    geom_bar(stat = "identity")+
    #coord_trans(x='log')+
    #coord_polar()+
    #scale_fill_viridis(option = "A")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="Income Range",
         subtitle = "The income range of the borrower at the time the listing was created.",
         x="Income Range",
         y="Count",
         fill="Sqrt(Count)")
```

EmploymentStatusDuration
The length in months of the employment status at the time the listing was created.

```{r}
RawData%>%
  filter(is.finite(EmploymentStatusDuration))%>%
  ggplot(aes(x=EmploymentStatusDuration))+
  geom_histogram(binwidth = 10,fill="#563ec3")+
   theme_minimal()+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="Income Range",
         subtitle = "The length in months of the employment status at the time the listing was created.",
         x="Inocme Range",
         y="Count",
         fill="Sqrt(Count)")
```




BorrowerRate

The Borrower's interest rate for this loan. 

```{r}
BorrowerRate=RawData$BorrowerRate
RawData%>%
  filter(BorrowerRate>quantile(BorrowerRate,0.01))%>%
  filter(BorrowerRate<quantile(BorrowerRate,0.99))%>%
  #count(BorrowerRate)%>%
  ggplot(aes(x=BorrowerRate))+
    geom_histogram(bins=40,fill="#563ec3")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="The Borrower's interest rate for this loan.  ", x="Borrower Rate", y="Count")

```

LoanOriginalAmount
```{r}
RawData%>%
  filter(LoanOriginalAmount!=0)%>%
  ggplot(aes(x = LoanOriginalAmount))+
  geom_density()
  

```
```{r}

```


Prosper Rating :
The Prosper Rating assigned at the time the listing was created between AA - HR.  Applicable for loans originated after July 2009.
```{r}
#levels(RawData$ProsperRating..Alpha.)
RawData %>%
  filter(RawData$ProsperRating..Alpha.!="")%>%
  #filter(RawData$ListingCreationDate>2009)
  count(ProsperRating..Alpha.) %>% 
  #mutate(IncomeRange=reorder(IncomeRange,-n))%>% 
  #filter(n>quantile(n,0.20))%>%
  ggplot(aes(x=ProsperRating..Alpha., y = n,fill=sqrt(n)))+
    geom_bar(stat = "identity")+
    theme_minimal()+
    theme(axis.text.x = element_text( ))+
    labs(title="Prosper Rating", x="Prosper Rating", y="Count",fill="Sqrt(Count)")
```

Monthly Loan Payment

```{r}

MonthlyLoanPayment=RawData$MonthlyLoanPayment

RawData%>%
  filter(MonthlyLoanPayment>quantile(MonthlyLoanPayment,0.01))%>%
  filter(MonthlyLoanPayment<quantile(MonthlyLoanPayment,0.99))%>%
  ggplot(aes(x=MonthlyLoanPayment))+
    geom_histogram(bins=100,fill="#563ec3")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="The scheduled monthly loan payment.", x="Monthly Loan Payment", y="Count")


```





```{r}
RawData%>%
  filter(MonthlyLoanPayment>125)%>%
  filter(MonthlyLoanPayment<200)%>%
  ggplot(aes(x=MonthlyLoanPayment))+
    geom_histogram(bins=300,fill="#563ec3")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="The scheduled monthly loan payment", x="Monthly Loan Payment", y="Count")

```


CreditGrade
```{r}
RawData%>%
  filter(CreditGrade!="")%>%
  count(CreditGrade) %>% 
  ggplot(aes(x=CreditGrade, y = n,fill=sqrt(n)))+
    geom_bar(stat = "identity")+
    theme_minimal()+
    theme(axis.text.x = element_text( ))+
    labs(title="CreditGrade", x="CreditGrade", y="Count",fill="Sqrt(Count)")

```

LP InterestandFees

Pre charge-off cumulative interest and fees paid by the borrower. If the loan has charged off, this value will exclude any recoveries.

```{r}
RawData%>%
  #filter(LP_InterestandFees>quantile(MonthlyLoanPayment,0.001))%>%
  #filter(LP_InterestandFees<quantile(MonthlyLoanPayment,0.999))%>%
  ggplot(aes(x=LP_InterestandFees))+
    geom_histogram(bins=300,fill="#d53e6c")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="Pre charge-off cumulative interest and fees paid by the borrower", x="LP InterestandFees", y="Count")


```
```{r}

RawData%>%
  filter(LP_InterestandFees>quantile(MonthlyLoanPayment,0.001))%>%
  filter(LP_InterestandFees<5000)%>%
  #filter(LP_InterestandFees<quantile(MonthlyLoanPayment,0.999))%>%
  ggplot(aes(x=LP_InterestandFees))+
    geom_histogram(bins=300,fill="#d53e6c")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="Pre charge-off cumulative interest and fees paid by the borrower", x="LP InterestandFees", y="Count")
```




Investors
The number of investors that funded the loan.
```{r}
Investors=RawData$Investors

RawData%>%
  #filter(Investors>quantile(Investors,0.03))%>%
  #filter(Investors<600)%>%
  filter(Investors<quantile(Investors,0.97))%>%
  ggplot(aes(x=Investors))+
    geom_histogram(bins=100,fill="#356e9c")+
    theme_minimal()+
    coord_trans(y="sqrt")+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="Investors",
         subtitle="The number of investors that funded the loan.",
         x="Investors",
         y="Count")

```


Employment Status Duration
The length in months of the employment status at the time the listing was created.




```{r}

EmploymentStatusDuration=RawData$EmploymentStatusDuration
RawData%>%
  filter(is.finite(EmploymentStatusDuration))%>%
  filter(EmploymentStatusDuration>quantile(EmploymentStatusDuration,0.04))%>%
  filter(EmploymentStatusDuration<quantile(EmploymentStatusDuration,0.96))%>%
  ggplot(aes(EmploymentStatusDuration))+
  geom_histogram(bins=156,fill="#c54e74")+
  labs(title="Employment Status Duration",
         subtitle="The length in months of the employment status at the time the listing was created.",
         x="Employment Status Duration",
         y="Count")
  
```

DebtToIncomeRatio
The debt to income ratio of the borrower at the time the credit profile was pulled. This value is Null if the debt to income ratio is not available. This value is capped at 10.01 (any debt to income ratio larger than 1000% will be returned as 1001%).

```{r}
RawData%>%
  filter(is.finite(DebtToIncomeRatio))%>%
  filter(DebtToIncomeRatio>quantile(DebtToIncomeRatio,0.01))%>%
  filter(DebtToIncomeRatio<quantile(DebtToIncomeRatio,0.99))%>%
  ggplot(aes(DebtToIncomeRatio))+
  geom_histogram(binwidth = 0.01,fill="#465498")

```


# Univariate Analysis


we can see alot of information from the previos section,
some propierts was expected others was a little superising 

examples : 
It was expected to get some pattern in loan value to tend to get some 
pattern (1000 , 5000 , 10000, 15000 )
personally I was expecte a equal distrupitoin in loan Term, 
nevertheless it was manily in 36 monthes 
the in come range for the borrower is normally distrupited as expected
the most interesting thing was the mode in monthly loan payment 
around 175 $ I think there is some requlation 
in united state reinforce  this amount of monthly payment.
something unexpect also the drop in the entreing date between 
2009 and 2010 I think this because of integration into
new system 




#Bivariate Plots Section


Year and Investor per loan
```{r echo=FALSE, Univariate_Plots}

RawData%>%
  ggplot(aes(x=ListingCreationDate,fill=LoanStatus))+
  geom_histogram(bins=100)+
  coord_trans(y="sqrt")+
  labs(title="Running Loan ",
       subtitle="that funded the loan.",
       x="Listing Creation Date",
       y="Count",
       fill="Loan Status")

```
 



```{r}


RawData%>%
  filter(!IncomeRange %in% list("Not displayed","$0") )%>%
  ggplot(aes(x=ListingCreationDate,fill=reorder(IncomeRange,-table(IncomeRange)[IncomeRange])))+
  geom_histogram(bins=300)+
  coord_trans(y="sqrt")+
  scale_fill_brewer(palette = 1,direction = -1)+
  labs(title="Income Range in time ",
       subtitle="he income range of the borrower at the time the listing was created.",
       x="Listing Creation Date",
       y="Count",
       fill="IncomeRange")

```




```{r}

RawData%>%
  filter(!CreditGrade=="")%>%
  ggplot(aes(x=ListingCreationDate,fill=CreditGrade))+
  geom_histogram(bins=300)+
  coord_trans(y="sqrt")+
  scale_fill_brewer(palette = 3,type = "div",direction = -1)+
  labs(title="CreditGrade ",
       subtitle="The Credit rating that was assigned at the time the listing went live. Applicable for listings pre-2009",
       x="Listing Creation Date",
       y="Count",
       fill="CreditGrade")

```
```{r}
RawData%>%
  filter(!CreditGrade=="")%>%
  ggplot(aes(x=ListingCreationDate,fill=CreditGrade))+
  geom_density(alpha=0.4)+
  scale_fill_brewer(palette ="Set3" ,type = "seq",direction = -1)+
  labs(title="CreditGrade ",
       subtitle="The Credit rating that was assigned at the time the listing went live. Applicable for listings pre-2009",
       x="Listing Creation Date",
       y="Count",
       fill="CreditGrade")
```

Monthly Loan Payment  vs time
```{r}
RawData %>%
  filter(MonthlyLoanPayment>quantile(MonthlyLoanPayment,0.02))%>%
  filter(MonthlyLoanPayment<quantile(MonthlyLoanPayment,0.98))%>%
  ggplot(aes(x=ListingCreationDate,y=MonthlyLoanPayment))+
  geom_jitter(alpha=0.01,color="red")+
  geom_smooth(method="auto",level=0.5,span=0.3,n=100)

```


```{r}
topOcc=levels(reorder(RawData$Occupation, -table(RawData$Occupation)[RawData$Occupation]))[0:15]
RawData%>%
  filter(Occupation %in% topOcc)%>%
  ggplot(aes(x=reorder(Occupation, -table(Occupation)[Occupation]),fill=LoanStatus))+
  geom_bar()+
  coord_trans(y="sqrt")+
  theme(axis.text.x = element_text(size=6, angle=90,hjust = 1))+
  #scale_fill_brewer(palette = "Spectral")+
  labs(title="Occupation ", x="Occupation", y="Count",fill=" Loan Status")
```

levels(RawData$LoanStatus)<-c(
                              "Completed",
                              "Cancelled",
                              "Chargedoff",
                              "Current",
                              "Defaulted",
                              "FinalPaymentInProgress",
                              "Past Due (1-15 days)",
                              "Past Due (16-30 days)",
                              "Past Due (31-60 days)",
                              "Past Due (61-90 days)",
                              "Past Due (91-120 days)",
                              "Past Due (>120 days)"
                              )

levels(RawData$LoanStatus)


```{r}
topOcc=levels(reorder(RawData$Occupation,+-table(RawData$Occupation)[RawData$Occupation]))[0:19]
RawData %>%
  filter(LoanStatus!="Defaulted")%>%
  filter(Occupation %in% topOcc)%>%
  #filter(!Occupation=="")%>%
  #filter(!LoanStatus=="")%>%
  count(Occupation,LoanStatus)%>%
  ggplot(aes(x=reorder(Occupation, -table(Occupation)[Occupation]),fill=LoanStatus,y=n))+
    geom_bar(stat = "identity")+
    coord_trans(y="sqrt")+
    theme(axis.text.x = element_text(size=6, angle=90,hjust = 1))+
    scale_fill_brewer(palette = "RdYlBu")+
    labs(title="Occupation ", x="Occupation", y="Count",fill=" Loan Status")
```


topOcc=levels(reorder(RawData$Occupation,+-table(RawData$Occupation)[RawData$Occupation]))[0:19]
RawData %>%
  filter(LoanStatus!="Defaulted")%>%
  filter(Occupation %in% topOcc)%>%
  #filter(!Occupation=="")%>%
  #filter(!LoanStatus=="")%>%
  count(Occupation,LoanStatus)%>%
  ggplot(aes(x=reorder(Occupation, -table(Occupation)[Occupation]),fill=LoanStatus,y=n))+
    geom_bar(stat = "identity")+
    coord_trans(y="sqrt")+
    theme(axis.text.x = element_text(size=6, angle=90,hjust = 1))+
    scale_fill_brewer(palette = "RdYlBu")+
    labs(title="Occupation ", x="Occupation", y="Count",fill=" Loan Status")
    
Term vs Time Creating, 




Term vs Investors


```{r}
RawData%>%
  
  ggplot(aes(x=LoanOriginalAmount, y=as.factor(Term), fill=0.5 - abs(0.5-..ecdf..))) +
    stat_density_ridges(geom = "density_ridges_gradient", calc_ecdf = TRUE) +
    scale_fill_viridis(name = "Tail probability", direction = -1)+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="Investors",
         subtitle="The number of investors that funded the loan.",
         x="Investors",
         y="Term")
```
DebtToIncomeRatio vs BorrowerRate

  
RawData%>%
  filter(BorrowerRate>quantile(BorrowerRate,0.01))%>%
  filter(BorrowerRate<quantile(BorrowerRate,0.99))%>%
  #count(BorrowerRate)%>%
  ggplot(aes(x=BorrowerRate))+
    geom_histogram(bins=40,fill="#563ec3")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = , angle= 45, hjust=1))+
    labs(title="The Borrower's interest rate for this loan.  ", x="Borrower Rate", y="Count")

```{r}
RawData%>%
  filter(is.finite(DebtToIncomeRatio))%>%
  filter(DebtToIncomeRatio>quantile(DebtToIncomeRatio,0.01))%>%
  filter(DebtToIncomeRatio<quantile(DebtToIncomeRatio,0.99))%>%
  filter(BorrowerRate>quantile(BorrowerRate,0.01))%>%
  filter(BorrowerRate<quantile(BorrowerRate,0.99))%>%
  ggplot(aes(x=DebtToIncomeRatio,y=BorrowerRate))+
    geom_jitter(alpha=0.05,color="#f65436")+
    geom_smooth()
    


  
```
```{r}
cor.test(RawData$DebtToIncomeRatio,RawData$BorrowerRate)
```


```{r}
RawData%>%
  filter(is.finite(LoanOriginalAmount))%>%
  filter(LoanOriginalAmount>quantile(LoanOriginalAmount,0.01))%>%
  filter(LoanOriginalAmount<quantile(LoanOriginalAmount,0.99))%>%
  filter(BorrowerRate>quantile(BorrowerRate,0.01))%>%
  filter(BorrowerRate<quantile(BorrowerRate,0.99))%>%
  ggplot(aes(x=LoanOriginalAmount,y=BorrowerRate))+
    geom_point(alpha=0.05,color="#f65436")+
    geom_smooth()

```


```{r}
cor.test(RawData$LoanOriginalAmount,RawData$BorrowerRate)
```
#Bivariate Analysis

what interesing her that in creditGrade there was type NC only before 2009 



# Multivariate Plots Section
ocppuaptin

```{r}
RawData%>%
  filter(Occupation %in% topOcc)%>%
  ggplot(aes(x=reorder(Occupation,-table(Occupation)[Occupation]),
             y=LoanOriginalAmount,
             fill=reorder(EmploymentStatus,-table(EmploymentStatus)[EmploymentStatus])
             ))+
    #geom_bar(stat="identity",alpha=0.5)+
    geom_bar(stat="identity")+
    scale_fill_viridis_d(option = "D",direction = -1)+
    #coord_trans(y="sqrt")+
    theme(axis.text.x = element_text(size=6, angle=90,hjust = 1))+
    labs(title="Occupation, Employment status, and total orignal ammont", 
         x="Occupation",
         y="Total Original Amount",
         fill=" EmploymentStatus")
    

```


```{r}

RawData%>%
  filter(ProsperRating..Alpha.!="")%>%
  filter(is.finite(MonthlyLoanPayment))%>%
  filter(BorrowerRate>quantile(BorrowerRate,0.01))%>%
  filter(BorrowerRate<quantile(BorrowerRate,0.99))%>%
  filter(MonthlyLoanPayment>quantile(MonthlyLoanPayment,0.01))%>%
  filter(MonthlyLoanPayment<quantile(MonthlyLoanPayment,0.99))%>%
  #filter(Investors>quantile(Investors,0.01))%>%
  #filter(Investors<quantile(Investors,0.99))%>%
  #filter(LoanOriginalAmount!=0)%>%
  ggplot(aes(y=MonthlyLoanPayment	,x=BorrowerRate  ,color=ProsperRating..Alpha.  ))+
      geom_point(alpha=0.2)+
      scale_color_viridis_d(option = "D")+
      #coord_trans(y="sqrt")+
      theme(axis.text.x = element_text(size=6, angle=0.1,hjust = 1))+
      labs(title="BorrowerRate,Monthly Loan Payment, Prosper Rating", 
           x="Borrower Rate",
           color="Prosper Rating ",
           y="Monthly Loan Payment",
           alpha=1)

```


# Multivariate Analysis
we can see the pattern in between montly loan payment , borrower rate and the proposer rate.


------

# Final Plots and Summary.

### Plot One
```{r}

RawData %>%
  filter(Occupation!="Other" )%>%
  filter(Occupation!="Professional" )%>%
  filter(Occupation!="")%>%
  count(Occupation) %>% 
  mutate(Occupation=reorder(Occupation,-n))%>% 
  filter(n>quantile(n,0.70))%>%
  ggplot(aes(x=Occupation, y = n,fill=sqrt(n)))+
    geom_bar(stat = "identity")+
    #scale_fill_viridis(option = "D")+
    theme_minimal()+
    theme(axis.text.x = element_text(size = 8, angle= 60, hjust=1))+
    labs(title="Occupation ", x="Occupation", y="Count",fill="Sqrt(Count)")
```

this plot describe what is the distruption of loans count regarding 
the profession after discared the misinformative occpuation like (other, profession)
so we can suggest wich field of worker in the next campigns to target to get
some more sales 




### Plot Two
```{r}

RawData%>%
  ggplot(aes(x=ListingCreationDate,fill=as.factor(Term)))+
  geom_density(alpha=0.6)+
  scale_fill_brewer(palette = "Set2",direction = 1)+
  labs(title="Term ",
       subtitle="The length of the loan expressed in months.",
       x="Listing Creation Date",
       y="Density",
       fill="CreditGrade")


```

In this plot we can answer our quesiotn in univaraible examination 
which was a little bit surprising why the 36 is the most likable loan
we can see that other types are only started after 2009 ( maybe of reugaltion)
also the other type of loan ( 12 ) is no available any more inspite of
it was very popular I think there's  a good markt opprtuinity in prompt again
this type of Loan



### Plot LoanOriginalAmount	vs MonthlyLoanPayment	, Term
```{r}

RawData%>%
  filter(MonthlyLoanPayment>quantile(MonthlyLoanPayment,0.01))%>%
  filter(MonthlyLoanPayment<quantile(MonthlyLoanPayment,0.99))%>%
  filter(LoanOriginalAmount!=0)%>%
  ggplot(aes(y=LoanOriginalAmount,x=MonthlyLoanPayment,color=as.factor(Term)))+
      geom_point(alpha=0.3)+
      scale_color_viridis_d(option="D")+
      scale_fill_viridis_d(option = "D",direction = -1)+
      #coord_trans(y="sqrt")+
      theme(axis.text.x = element_text(size=6, angle=90,hjust = 1))+
      labs(title="Occupation, Employment status, and loan orignal ammont", 
           x="Monthly Loan Payment",
           y="Loan Original Amount",
           color="Term in Monthes")

```


In the preivous plot we can easly see the relation between the three variabls and the lineartiy is obvious 


------

# Reflection
we have explored myn variabls  and this data set is really very informative,
I wish i had the time to dig more and explore an extra ready variblas or 
calculated supported ones espeically the last plot descripe the realtion between the variables
